Trip Summary ITHIM-R

### 2021-03-17 code/producing_trips_rd/trip-summary.Rmd
Updating detail table

@@

@@

  Trip_Stage = c("Stage", "Trip", "Stage", "Stage", "Trip", 

@@

  Stage_missing = c("N/A", 

@@

@@

              "Looks like the survey capture up to 5 stage modes, but duration was not asked."),

@@

@@

>>>>

    # Mexico city

@@

    # Bogota

@@

  Trip_Stage = c("Stage", "Trip", "Trip", "Stage", "Trip", 

@@

  Stage_missing = c(

@@

    "No stage information", 
    # Mexico city

@@

    "Looks like the survey capture up to 5 stage modes, but duration was not asked."
    ),

@@

                             "Not included",
                             "Not sure, yet.",
                             "Not sure, yet",

@@

           # Belo horizonte: page 81, "Codebook and protocol.pdf"
